---
title: 'Nachos by Nina Dyatchenko'
subtitle: 'BST692'
date: "`r format(Sys.time(), '%B %d %Y')`"
output: html_document

---

---
Comments: Seting Report borders style
---
<style type = "text/css"> ### 
  .main-container {
    max-width: 1800px;
    margin-left: auto;
    margin-right: auto;
  }
pre {
  border: 0;
}
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
Downloading data from REDCap
---
```{r include=FALSE}
#Clear existing data and graphics
rm(list=ls())
graphics.off()

#Load Hmisc library
library(Hmisc)

#Read Data
data = read.csv('NachoCravingIndex_DATA_2019-06-12_1449.csv')

#Setting Labels
label(data$record_id)="Record ID"
label(data$nci_timestamp)="Survey Timestamp"
label(data$nachos)="Have you ever eaten nachos?"
label(data$treat)="I use nachos to treat a medical condition (other than hunger)."
label(data$treating)="What is the primary problem that nachos are treating?"
label(data$othercondition)="What other condition?"
label(data$last)="When did you last eat nachos?"
label(data$traveled)="Have you traveled somewhere specifically to get nachos?"
label(data$miles)="What is the farthest distance (in miles) you have traveled toget nachos? A calculator to convert kilometers to miles is here."
label(data$now)="Are you currently craving nachos?"
label(data$strong)="How extreme is your current nacho craving?"
label(data$ingredients___1)="What ingredients do you currently crave? (choice=Chips)"
label(data$ingredients___2)="What ingredients do you currently crave? (choice=Yellow cheese)"
label(data$ingredients___3)="What ingredients do you currently crave? (choice=Orange cheese)"
label(data$ingredients___4)="What ingredients do you currently crave? (choice=White cheese)"
label(data$ingredients___5)="What ingredients do you currently crave? (choice=Meat)"
label(data$ingredients___6)="What ingredients do you currently crave? (choice=Beans)"
label(data$ingredients___7)="What ingredients do you currently crave? (choice=Tomatoes)"
label(data$ingredients___8)="What ingredients do you currently crave? (choice=Peppers)"
label(data$cheese)="The cheesy goodness"
label(data$crunch)="The crunchy goodness"
label(data$bean)="The beany goodness"
label(data$guacamole)="The guacamole goodness"
label(data$jalapeno)="The jalapeno goodness"
label(data$meat)="The meaty goodness"
label(data$life)="How have nachos changed your life?"
label(data$nci_complete)="Complete?"
#Setting Units


#Setting Factors(will create new variable for factors)
data$nachos.factor = factor(data$nachos,levels=c("1","0"))
data$treat.factor = factor(data$treat,levels=c("1","0"))
data$treating.factor = factor(data$treating,levels=c("1","2","3"))
data$last.factor = factor(data$last,levels=c("1","2","3","4","5","6"))
data$traveled.factor = factor(data$traveled,levels=c("1","0"))
data$now.factor = factor(data$now,levels=c("1","0"))
data$ingredients___1.factor = factor(data$ingredients___1,levels=c("0","1"))
data$ingredients___2.factor = factor(data$ingredients___2,levels=c("0","1"))
data$ingredients___3.factor = factor(data$ingredients___3,levels=c("0","1"))
data$ingredients___4.factor = factor(data$ingredients___4,levels=c("0","1"))
data$ingredients___5.factor = factor(data$ingredients___5,levels=c("0","1"))
data$ingredients___6.factor = factor(data$ingredients___6,levels=c("0","1"))
data$ingredients___7.factor = factor(data$ingredients___7,levels=c("0","1"))
data$ingredients___8.factor = factor(data$ingredients___8,levels=c("0","1"))
data$cheese.factor = factor(data$cheese,levels=c("1","2","3","4","5"))
data$crunch.factor = factor(data$crunch,levels=c("1","2","3","4","5"))
data$bean.factor = factor(data$bean,levels=c("1","2","3","4","5"))
data$guacamole.factor = factor(data$guacamole,levels=c("1","2","3","4","5"))
data$jalapeno.factor = factor(data$jalapeno,levels=c("1","2","3","4","5"))
data$meat.factor = factor(data$meat,levels=c("1","2","3","4","5"))
data$nci_complete.factor = factor(data$nci_complete,levels=c("0","1","2"))

levels(data$nachos.factor)=c("Yes","No")
levels(data$treat.factor)=c("True","False")
levels(data$treating.factor)=c("Asthma","Cancer","Other")
levels(data$last.factor)=c("I am currently eating nachos.","I ate nachos earlier today.","I ate nachos this week.","I ate nachos in the last month.","I ate nachos in the last year.","I ate nachos more than a year ago.")
levels(data$traveled.factor)=c("Yes","No")
levels(data$now.factor)=c("Yes","No")
levels(data$ingredients___1.factor)=c("Unchecked","Checked")
levels(data$ingredients___2.factor)=c("Unchecked","Checked")
levels(data$ingredients___3.factor)=c("Unchecked","Checked")
levels(data$ingredients___4.factor)=c("Unchecked","Checked")
levels(data$ingredients___5.factor)=c("Unchecked","Checked")
levels(data$ingredients___6.factor)=c("Unchecked","Checked")
levels(data$ingredients___7.factor)=c("Unchecked","Checked")
levels(data$ingredients___8.factor)=c("Unchecked","Checked")
levels(data$cheese.factor)=c("1 Dont like","2","3 Neutral","4","5 Love it")
levels(data$crunch.factor)=c("1 Dont like","2","3 Neutral","4","5 Love it")
levels(data$bean.factor)=c("1 Dont like","2","3 Neutral","4","5 Love it")
levels(data$guacamole.factor)=c("1 Dont like","2","3 Neutral","4","5 Love it")
levels(data$jalapeno.factor)=c("1 Dont like","2","3 Neutral","4","5 Love it")
levels(data$meat.factor)=c("1 Dont like","2","3 Neutral","4","5 Love it")
levels(data$nci_complete.factor)=c("Incomplete","Unverified","Complete")
```


Describe the variable: “When did you last eat nachos?” using a well-formatted table.
```{r include=FALSE}

library(stringr)
library(janitor)

taybull <- function(variable, subset = FALSE) {
  theLab <- label(variable)
  theLab2 <- str_sub(theLab, str_locate(theLab, "=")[,1]+1, str_locate(theLab, "\\)")[,1]-1)
  if(subset == FALSE){ 
      cat(paste(theLab, "\n"))
    } else {
      cat(paste(theLab2, "\n"))
    }
  Response <- as.name(paste0(deparse(substitute(variable)), ".factor"))
  Response <- eval(parse(text = Response))
  tabyl(Response)
}
```

```{r comment=NA,echo=FALSE}
taybull(data$last) %>% 
  adorn_pct_formatting(digits = 0)
```

Make a binary word of the pattern for “What ingredients do you currently crave?” <br/>
C - Chips <br/>
Y - Yellow cheese <br/>
O - Orange cheese <br/>
W - White cheese <br/>
M - Meet <br/>
B - Beans <br/>
T - Tomatoes <br/>
P - Peppers <br/>

```{r include=FALSE}

library(dplyr)
data <- data %>%
  mutate(word = paste0(
    case_when(ingredients___1 == 0 ~ "_",
              ingredients___1 == 1 ~ "C",  # Chips
              TRUE ~ "."),
    case_when(ingredients___2 == 0 ~ "_",
              ingredients___2 == 1 ~ "Y",  # Yellow cheese
              TRUE ~ "."),
    case_when(ingredients___3 == 0 ~ "_",
              ingredients___3 == 1 ~ "O",  # Orange cheese
              TRUE ~ "."),
    case_when(ingredients___4 == 0 ~ "_",
              ingredients___4 == 1 ~ "W",  # White cheese
              TRUE ~ "."),
    case_when(ingredients___5 == 0 ~ "_",
              ingredients___5 == 1 ~ "M",  # Meet
              TRUE ~ "."),
    case_when(ingredients___6 == 0 ~ "_",
              ingredients___6 == 1 ~ "B",  # Beans
              TRUE ~ "."),
    case_when(ingredients___7 == 0 ~ "_",
              ingredients___7 == 1 ~ "T",  # Tomatos
              TRUE ~ "."),
    case_when(ingredients___8 == 0 ~ "_",
              ingredients___8 == 1 ~ "P",  # Peppers
              TRUE ~ ".")
  ))
```

```{r comment=NA,echo=FALSE}
#factor(data$word)
#label(data$word)="What ingredients do you currently crave?"

#data$word.factor = factor(data$word,levels=c("0","1"))

tabyl(data$word) %>%
  adorn_pct_formatting(digits = 1)

#taybull(data$word) %>%
 # adorn_pct_formatting(digits = 1)

#names(data$word) <- "New"
```


---
Creating dataset using Miami.edu API Token
---

```{r include=FALSE}

library(redcapAPI)
rcon <- redcapConnection(url = 'https://redcap.miami.edu/api/', 
                         token = '2D82594D583F3F1CA719EC868197F9BD')

# Creating the exported data:
data2 <- exportRecords(rcon)
```



